CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-18 paper/ms.tex
Add four fake stars to diagnose
Grammar fixed

Comparison of the spectrum if we set the parameters showed in old figure 8. In old figure 8, the red line and the green line are on the top of each other
 \bigskip

@@

\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters showed in old figure 8}
\bigskip

 Comparison of the spectrum if we set the parameters showed in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
 \bigskip

@@

\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters showed in old figure 9}
\bigskip

@@

>>>>

Comparison of the spectrum if we set the parameters shown in old figure 8. In old figure 8, the red line and the green line are on the top of each other
 \bigskip

@@

\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters shown in old figure 8}
\bigskip

 Comparison of the spectrum if we set the parameters shown in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
 \bigskip

@@

\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters shown in old figure 9}
\bigskip

@@

In diagnostic plot 5, I use four fake stars. The data spectra of these four stars are generated by moving their inferred spectra one pixel left. If my new code is right, a, b and c will be [1,0,0]. In diagnostic figure 5, a=1, b=0 and c=0.
\bigskip

\includegraphics[width=170mm]{d_figure_5.png}
\bigskip

\centerline{Diagnostic Fig.5 Comparison of the spectrum for the four fake stars}
\bigskip
